### 2009-02-25 doc/ws-programming-tutorial/doc/tex_introduction/introduction.tex
Started outline for the TLS echo service
echo.wsdl

>>>>

\task{Provide a list of modules to be loaded! Along with the implemented functionality which can be addressed with XML elements!!}
    mcctcp\\
\begin{verbatim}
<tcp:Listen>
	<tcp:Port>60000</tcp:Port>
	<tcp:Version>4</tcp:Version>
</tcp:Listen>
\end{verbatim}
    mcctls\\
\begin{verbatim}
 			<KeyPath>./clientKey.pem</KeyPath>
			<CertificatePath>./clientCert.pem</CertificatePath>
			<CACertificatePath>./clientCA.pem</CACertificatePath><!-- CACertificatesDir Should be /etc/... blub mention that-->

\end{verbatim}

    mcchttp\\
\begin{verbatim}
                      <next id="soap">POST</next>
                      <next id="plexer">GET</next>
                      <next id="plexer">PUT</next>
\end{verbatim}
    mccsoap\\
\begin{verbatim}
	???<ClientSSLConfig FromFile='filename'/>  
\end{verbatim}
